---
title: "GERMAN CREDIT RISK ANALYSIS AND PREDICTIVE MODELLING"
author: "Surya Sashank Gundepudi"
date: "9/26/2021"
output:
  html_document: 
    toc : TRUE
    toc_float : TRUE
    theme : "paper"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract
Currently there are many machine learning models that have been deployed to 
predict whether if a person will default their loan amount or they will pay it
back. These decisions are made using predictive modelling and ML by using 
various factors of the person, such as their education level, sex, 
personal status, checking amount, number of savings bonds and many 
more. The aim of this project to use one of such publicly available datasets, 
the *Statlog - German Credit Risk Dataset* which has anonymized data of many 
customers of a bank, with their personal details and whether if they had defaulted
their loan amount or they were good customers and paid back their loan amount. 
Within this project we aim to first pre-process the data into both user readable 
and machine readable format, explore the data and try to derive inferences, and 
finally use this to predict whether if a person will default their loan or not. 

**Keywords** - German-Credit-Risk, Machine-Learning, Predictive Modelling

## Introduction
Most banks' main source of income is from providing loans for their customers. 
They store people's money and pay them some interest on that money, and to some
other customers they provide a loan for a purpose at a higher interest than 
before. This margin between the saving interest and loan interest is where banks
make most of their money. 

But every time a bank provides a loan it is facing a risk of the loan not being 
paid back. Generally, banks take some type of collateral such as a person's 
property. However, most banks would want to even avoid providing a person who
will default their loan since they are losing money and time value of money. 
In that time they could have invested in a loan to a person who will pay their
loan. 

Therefore, it is crucial to determine whether if a person is a defaulter or 
someone who will pay back their loan before the bank even provides the loan. In
this project I try to pre-process the data, then plot graphs using the powerful 
R Programming Language and the *plotly* package. Using these graphs I will try 
to derive inferences from these plots and finally use the data to build a machine
learning model that predicts whether if a person will be a defaulter or not. 

## Dataset Description 

This dataset was provided by Dr. Hand Hoffmann from the University of Hamburg 
(Universit"at Hamburg). It is publicily available for data scientists to use at the 
[UCI MACHINE LEARNING REPOSITOY](https://archive.ics.uci.edu/ml/index.php). The
direct link to the dataset, with both numeric and the true data, is at -  [STATLOG-GERMAN-CREDIT](https://archive.ics.uci.edu/ml/datasets/statlog+(german+credit+data))


## Including Plots

You can also embed plots, for example:

Testing plotly

```{r, echo=FALSE, include=FALSE}
library(dplyr)
library(plotly)
library(ggplot2)
library(reshape2)
library(tidyr)
library(descr)

data <- read.csv("data/eda-german-credit.csv")
fig1 <- plot_ly(
  data = data, 
  x = c("Good", "Bad"), 
  y = c(length(data$Outcome[data$Outcome == "Good"]), 
        length(data$Outcome[data$Outcome == "Bad"])),  
  type = "bar", 
  marker = list(color = c("Green", "Red"))
)

fig1 <- fig1 %>%   layout(
  title = 'Target Variable Distribution', 
  xaxis = list(title = 'Outcome of Risk Taken'), 
  font=t, 
  plot_bgcolor = "#e5ecf6",
  yaxis = list(title = 'Count'), 
  legend = list(title=list(text='Legend Title')))

```

Now including the plot
```{r}
# Un-comment this line to get the figure
fig1
```